---
title: "Simulation_first_draft"
output: html_document
date: '2023-02-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(car) # For Anova()
library(nnet) # For multinom()
```

```{r}
set.seed(13032023)

# Load population file
load("F:/Thesis Project/R code/Main_draft/population_data.RData")

```




# 1. Predictors Influence on Outcome Y

Analysis of impact of X variables on Y with type II and type III Likelihood 
Ratio Test.

## 1.1. n = 50


```{r}
set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeII_p <- list() # list for p-values
anova_typeII_LRT <- list() # list for LRT statistic

# Type II test is repeated it = 300 times
for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  multinom_model <- multinom(y ~ x1 + x2 + x3 + x4, data = sample_data)
  anova_typeII_p[[i]] <- Anova(multinom_model, type = 2)$"Pr(>Chisq)" # p-value
  anova_typeII_LRT[[i]] <- Anova(multinom_model, type = 2)$"LR Chisq" # LRT
}

anova_typeII_p <- do.call(cbind, anova_typeII_p)
anova_typeII_p_avg <- rowMeans(anova_typeII_p) # average of the p-values
anova_typeII_p_sd <-  apply(anova_typeII_p, 1, sd) # SD of the p-values
# significance rate
anova_typeII_sig  <- apply(anova_typeII_p, 1, function(x) sum(x < .05) /it)
# average LRT statistic
anova_typeII_LRT <- rowMeans(do.call(cbind, anova_typeII_LRT))

```





```{r}
set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times sample is taken and ANOVA is repeated

anova_typeIII_p <- list() # list for p-values
anova_typeIII_LRT <- list() # list for LRT statistic

# Type III test repeated it = 300 times
for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  multinom_model <- multinom(y ~ x1 + x2 + x3 + x4, data = sample_data)
  anova_typeIII_p[[i]] <- Anova(multinom_model, type = 3)$"Pr(>Chisq)" # p-value
  anova_typeIII_LRT[[i]] <- Anova(multinom_model, type = 3)$"LR Chisq" # LRT
}

anova_typeIII_p <- do.call(cbind, anova_typeIII_p) 
anova_typeIII_p_avg <- rowMeans(anova_typeIII_p) # average of the p-values
anova_typeIII_p_sd <-  apply(anova_typeIII_p, 1, sd) # SD of the p-values
# significance rate
anova_typeIII_sig  <- apply(anova_typeIII_p, 1, function(x) sum(x < .05) /it)
# average LRT statistic
anova_typeIII_LRT <- rowMeans(do.call(cbind, anova_typeIII_LRT))

```


```{r}
print("Results for Type II LRT")
round(anova_typeII_p_avg, 3)
round(anova_typeII_p_sd, 2)
round(anova_typeII_sig, 2)  
round(anova_typeII_LRT, 2) 

print("Results for Type III LRT")
round(anova_typeIII_p_avg, 3)
round(anova_typeIII_p_sd, 2)
round(anova_typeIII_sig , 2) 
round(anova_typeIII_LRT, 2)
```


## 1.2. n = 1000

```{r}
set.seed(13032023)
n <- 1000 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeII_p <- list()
anova_typeII_LRT <- list()

# Type II test repeated it = 300 times
for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  multinom_model <- multinom(y ~ x1 + x2 + x3 + x4, data = sample_data)
  anova_typeII_p[[i]] <- Anova(multinom_model, type = 2)$"Pr(>Chisq)" # p-value
  anova_typeII_LRT[[i]] <- Anova(multinom_model, type = 2)$"LR Chisq" # LRT
}

anova_typeII_p <- do.call(cbind, anova_typeII_p)
anova_typeII_p_avg <- rowMeans(anova_typeII_p) # average of the p-values
anova_typeII_p_sd <-  apply(anova_typeII_p, 1, sd) # SD of the p-values
# significance rate
anova_typeII_sig  <- apply(anova_typeII_p, 1, function(x) sum(x < .05) /it)
# average LRT statistic
anova_typeII_LRT <- rowMeans(do.call(cbind, anova_typeII_LRT))

```





```{r}
set.seed(13032023)
n <- 1000 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeIII_p <- list() # list for the p-values
anova_typeIII_LRT <- list() # list for the LRT statistic

# Type II test repeated it = 300 times
for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  multinom_model <- multinom(y ~ x1 + x2 + x3 + x4, data = sample_data)
  anova_typeIII_p[[i]] <- Anova(multinom_model, type = 3)$"Pr(>Chisq)" # p-value
  anova_typeIII_LRT[[i]] <- Anova(multinom_model, type = 3)$"LR Chisq" # LRT
}

anova_typeIII_p <- do.call(cbind, anova_typeIII_p)
anova_typeIII_p_avg <- rowMeans(anova_typeIII_p) # average of the p-values
anova_typeIII_p_sd <-  apply(anova_typeIII_p, 1, sd) # SD of the p-values
# significance rate
anova_typeIII_sig  <- apply(anova_typeIII_p, 1, function(x) sum(x < .05) /it) 
# average LRT statistic
anova_typeIII_LRT <- rowMeans(do.call(cbind, anova_typeIII_LRT))

```


```{r}
print("Results for Type II LRT")
round(anova_typeII_p_avg, 3)
round(anova_typeII_p_sd, 2)
round(anova_typeII_sig, 2)  
round(anova_typeII_LRT, 2) 

print("Results for Type III LRT")
round(anova_typeIII_p_avg, 3)
round(anova_typeIII_p_sd, 2)
round(anova_typeIII_sig , 2) 
round(anova_typeIII_LRT, 2)
```


# 2. Predictors Influence on Respomse Indicator R (when n = 50)

The sample size (n) needs to be changed to study the influence of predictors
on the response indicator in other sample sizes.

### 2.1.1 Response rate approximately 60%

```{r}
set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeII_p_R <- list() # list of p-values
anova_typeII_LRT_R <- list() # list of LRT statistic
typeII_avg_response_rate <- list() # list of response rates

# Type II test is repeated  it = 300 times
for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  
  # response probability for ARR 60%
  resp_prob <- (exp(-19.3 
                    + 1.5 * sample_data$x1 
                    + 2.5 * sample_data$x2 
                    + 1.2 * sample_data$x3) /
                  (1  + exp(-19.3 
                            + 1.5 * sample_data$x1
                            + 2.5 * sample_data$x2 
                            + 1.2 * sample_data$x3)))

  sample_data$response <- rbinom(nrow(sample_data), 1, resp_prob)

  glm_model <- glm(response ~ x1 + x2 + x3 + x4, 
                   data = sample_data, 
                   family = "binomial")
  anova_typeII_p_R[[i]] <- Anova(glm_model, type = 2)$"Pr(>Chisq)" # p-value
  anova_typeII_LRT_R[[i]] <- Anova(glm_model, type = 2)$"LR Chisq" # LRT
  typeII_avg_response_rate[[i]] <- sum(sample_data$response) / nrow(sample_data)
}

anova_typeII_p_R <- do.call(cbind, anova_typeII_p_R)
anova_typeII_p_avg_R <- rowMeans(anova_typeII_p_R) # average of the p-values
anova_typeII_p_sd_R <-  apply(anova_typeII_p_R, 1, sd) # SD of the p-values

# significance rate
anova_typeII_sig_R  <- apply(anova_typeII_p_R, 1, function(x) sum(x < .05) /it)
# average LRT statistic
anova_typeII_LRT_R <- rowMeans(do.call(cbind, anova_typeII_LRT_R))
# average response rate (ARR)
typeII_avg_response_rate  <- mean(unlist(typeII_avg_response_rate)) 



```


```{r}
set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeIII_p_R <- list()
anova_typeIII_LRT_R <- list()
typeIII_avg_response_rate <- list()

# Type III test is repeated  it = 300 times
for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  
  resp_prob <- (exp(-19.3 
                    + 1.5 * sample_data$x1 
                    + 2.5* sample_data$x2 
                    + 1.2 * sample_data$x3) /
                            (1 + exp(-19.3 
                                     + 1.5 * sample_data$x1 
                                     + 2.5* sample_data$x2 
                                     + 1.2 * sample_data$x3)))
  
  sample_data$response <- rbinom(nrow(sample_data), 1, resp_prob)

  glm_model <- glm(response ~ x1 + x2 + x3 + x4, data = sample_data, 
                   family = "binomial")
  anova_typeIII_p_R[[i]] <- Anova(glm_model, type = 3)$"Pr(>Chisq)"
  anova_typeIII_LRT_R[[i]] <- Anova(glm_model, type = 3)$"LR Chisq"
  typeIII_avg_response_rate[[i]]<- sum(sample_data$response) / nrow(sample_data)
}

anova_typeIII_p_R <- do.call(cbind, anova_typeIII_p_R)
anova_typeIII_p_avg_R <- rowMeans(anova_typeIII_p_R)
anova_typeIII_p_sd_R <-  apply(anova_typeIII_p_R, 1, sd)
anova_typeIII_sig_R  <- apply(anova_typeIII_p_R, 1, function(x) sum(x < .05) /it)
anova_typeIII_LRT_R <- rowMeans(do.call(cbind, anova_typeIII_LRT_R))
typeIII_avg_response_rate  <- mean(unlist(typeIII_avg_response_rate))

```


```{r}
print("Results for Type II LRT")
round(anova_typeII_p_avg_R, 3)
round(anova_typeII_p_sd_R, 2)
round(anova_typeII_sig_R, 2) 
round(anova_typeII_LRT_R, 2)
round(typeIII_avg_response_rate, 2)

print("Results for Type III LRT")
round(anova_typeIII_p_avg_R, 3)
round(anova_typeIII_p_sd_R, 2)
round(anova_typeIII_sig_R, 2)
round(anova_typeIII_LRT_R, 2)
round(typeIII_avg_response_rate, 2)
```


### 2.1.2 Response rate approximately 70%

```{r}
set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeII_p_R <- list()
anova_typeII_LRT_R <- list()
typeII_avg_response_rate <- list()

for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  
  resp_prob <-  (exp(-18.2 
                     + 1.5 * sample_data$x1 
                     + 2.5 * sample_data$x2 
                     + 1.2 * sample_data$x3) /
                            (1 + exp(-18.2 
                                     + 1.5 * sample_data$x1 
                                     + 2.5 * sample_data$x2 
                                     + 1.2 * sample_data$x3)))



  sample_data$response <- rbinom(nrow(sample_data), 1, resp_prob)

  glm_model <- glm(response ~ x1 + x2 + x3 + x4, data = sample_data, 
                   family = "binomial")
  anova_typeII_p_R[[i]] <- Anova(glm_model, type = 2)$"Pr(>Chisq)"
  anova_typeII_LRT_R[[i]] <- Anova(glm_model, type = 2)$"LR Chisq"
  typeII_avg_response_rate[[i]]<- sum(sample_data$response) / nrow(sample_data)
}

anova_typeII_p_R <- do.call(cbind, anova_typeII_p_R)
anova_typeII_p_avg_R <- rowMeans(anova_typeII_p_R)
anova_typeII_p_sd_R <-  apply(anova_typeII_p_R, 1, sd)
anova_typeII_sig_R  <- apply(anova_typeII_p_R, 1, function(x) sum(x < .05) /it)
anova_typeII_LRT_R <- rowMeans(do.call(cbind, anova_typeII_LRT_R))
typeII_avg_response_rate  <- mean(unlist(typeII_avg_response_rate))

```


```{r}

set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeIII_p_R <- list()
anova_typeIII_LRT_R <- list()
typeIII_avg_response_rate <- list()


for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  
  resp_prob <-(exp(-18.2 
                   + 1.5 * sample_data$x1 
                   + 2.5 * sample_data$x2 
                   + 1.2 * sample_data$x3) /
                            (1 + exp(-18.2 
                                     + 1.5 * sample_data$x1 
                                     + 2.5 * sample_data$x2 
                                     + 1.2 * sample_data$x3)))


  sample_data$response <- rbinom(nrow(sample_data), 1, resp_prob)

  glm_model <- glm(response ~ x1 + x2 + x3 + x4, data = sample_data, 
                   family = "binomial")
  anova_typeIII_p_R[[i]] <- Anova(glm_model, type = 3)$"Pr(>Chisq)"
  anova_typeIII_LRT_R[[i]] <- Anova(glm_model, type = 3)$"LR Chisq"
  typeIII_avg_response_rate[[i]]<- sum(sample_data$response) / nrow(sample_data)
}

anova_typeIII_p_R <- do.call(cbind, anova_typeIII_p_R)
anova_typeIII_p_avg_R <- rowMeans(anova_typeIII_p_R)
anova_typeIII_p_sd_R <-  apply(anova_typeIII_p_R, 1, sd)
anova_typeIII_sig_R  <- apply(anova_typeIII_p_R, 1, function(x) sum(x < .05) /it)
anova_typeIII_LRT_R <- rowMeans(do.call(cbind, anova_typeIII_LRT_R))
typeIII_avg_response_rate  <- mean(unlist(typeIII_avg_response_rate))

```


```{r}
print("Results for Type II LRT")
round(anova_typeII_p_avg_R, 3)
round(anova_typeII_p_sd_R, 2)
round(anova_typeII_sig_R, 2)  
round(anova_typeII_LRT_R, 2)
typeIII_avg_response_rate 

print("Results for Type III LRT")
round(anova_typeIII_p_avg_R, 3)
round(anova_typeIII_p_sd_R, 2)
round(anova_typeIII_sig_R, 2)
round(anova_typeIII_LRT_R, 2)
round(typeIII_avg_response_rate, 2) 
```



### 2.1.3 Response rate approximately 80%

```{r}
set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeII_p_R <- list()
anova_typeII_LRT_R <- list()
typeII_avg_response_rate <- list()

for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  
  resp_prob <- (exp(-17 
                    + 1.5 * sample_data$x1 
                    + 2.5 * sample_data$x2 
                    + 1.2 * sample_data$x3) /
                          (1 + exp(-17 
                                   + 1.5 * sample_data$x1 
                                   + 2.5 * sample_data$x2 
                                   + 1.2 * sample_data$x3)))


  sample_data$response <- rbinom(nrow(sample_data), 1, resp_prob)

  glm_model <- glm(response ~ x1 + x2 + x3 + x4, data = sample_data, 
                   family = "binomial")
  anova_typeII_p_R[[i]] <- Anova(glm_model, type = 2)$"Pr(>Chisq)"
  anova_typeII_LRT_R[[i]] <- Anova(glm_model, type = 2)$"LR Chisq"
  typeII_avg_response_rate[[i]]<- sum(sample_data$response) / nrow(sample_data)
}

anova_typeII_p_R <- do.call(cbind, anova_typeII_p_R)
anova_typeII_p_avg_R <- rowMeans(anova_typeII_p_R)
anova_typeII_p_sd_R <-  apply(anova_typeII_p_R, 1, sd)
anova_typeII_sig_R  <- apply(anova_typeII_p_R, 1, function(x) sum(x < .05) /it)
anova_typeII_LRT_R <- rowMeans(do.call(cbind, anova_typeII_LRT_R))
typeII_avg_response_rate  <- mean(unlist(typeII_avg_response_rate))

```


```{r}

set.seed(13032023)
n <- 50 # sample size
it <- 300 # number of times ANOVA is repeated

anova_typeIII_p_R <- list()
anova_typeIII_LRT_R <- list()
typeIII_avg_response_rate <- list()


for(i in 1:it){
  sample_data <- population[sample(1:nrow(population), n, replace = FALSE), ]
  
  resp_prob <-    resp_prob <- (exp(-17
                                    + 1.5 * sample_data$x1 
                                    + 2.5 * sample_data$x2 
                                    + 1.2 * sample_data$x3) /
                          (1 + exp(-17 
                                   + 1.5 * sample_data$x1 
                                   + 2.5 * sample_data$x2 
                                   + 1.2 * sample_data$x3)))


  sample_data$response <- rbinom(nrow(sample_data), 1, resp_prob)

  glm_model <- glm(response ~ x1 + x2 + x3 + x4, data = sample_data, 
                   family = "binomial")
  anova_typeIII_p_R[[i]] <- Anova(glm_model, type = 3)$"Pr(>Chisq)"
  anova_typeIII_LRT_R[[i]] <- Anova(glm_model, type = 3)$"LR Chisq"
  typeIII_avg_response_rate[[i]]<- sum(sample_data$response) / nrow(sample_data)
}

anova_typeIII_p_R <- do.call(cbind, anova_typeIII_p_R)
anova_typeIII_p_avg_R <- rowMeans(anova_typeIII_p_R)
anova_typeIII_p_sd_R <-  apply(anova_typeIII_p_R, 1, sd)
anova_typeIII_sig_R  <- apply(anova_typeIII_p_R, 1, function(x) sum(x < .05) /it)
anova_typeIII_LRT_R <- rowMeans(do.call(cbind, anova_typeIII_LRT_R))
typeIII_avg_response_rate  <- mean(unlist(typeIII_avg_response_rate))

```


```{r}
print("Results for Type II LRT")
round(anova_typeII_p_avg_R, 3)
round(anova_typeII_p_sd_R, 2)
round(anova_typeII_sig_R, 2)  
round(anova_typeII_LRT_R, 2)
typeIII_avg_response_rate 

print("Results for Type III LRT")
round(anova_typeIII_p_avg_R, 3)
round(anova_typeIII_p_sd_R, 2)
round(anova_typeIII_sig_R, 2)
round(anova_typeIII_LRT_R, 2)
round(typeIII_avg_response_rate, 2) 
```


